First Workshop on on Sustainable Software for Science: Practice and Experiences (WSSSPE): Overview and Summary

### 2014-01-21 WSSSPE1_report/WSSSPE1_summary_report.tex
fixing latex bug
initial organization

\author{TBD}

@@

@@

%\katznote{example comment by Dan}
%
%\gabnote{example comment by Gabrielle}
%
%\nchnote{example comment by Neil}
%
%\manishnote{example comment by Manish}
%
%\davidnote{example comment by David}

@@

\section{Submissions}

@@

\section{Peer-Review}

@@

\section{Results}

@@

>>>>

\author{Authors TBD}

@@

People who have volunteered to work on this report:

the workshop organizers:
\begin{itemize}
\item "Daniel S. Katz" <dkatz@nsf.gov>
\item Gabrielle Allen <gdallen@illinois.edu>
\item "Neil Chue Hong" <N.ChueHong@software.ac.uk>
\item Manish Parashar <parashar@rutgers.edu>
\item David Proctor <dproctor@nsf.gov>
\end{itemize}

and additional volunteers:
\begin{itemize}
\item Chris Mattmann <chris.a.mattmann@jpl.nasa.gov>
\item Ketan Maheshwari <ketancmaheshwari@gmail.com>
\item Marlon Pierce <marpierc@iu.edu>
\item Colin Venters <C.Venters@hud.ac.uk>
\item Suresh Marru <smarru@iu.edu>
\item Lynn Zentner <lzentner@purdue.edu>
\item Anne Elster <anne.elster@gmail.com>
\item Shel Swenson <mdswenso@usc.edu>
\item Andy Ray Terrel <andy.terrel@gmail.com>
\item Abani Patra <abani.patra@gmail.com>
\item Nancy Wilkins-Diehr <wilkinsn@sdsc.edu>
\item James Spencer <j.spencer@imperial.ac.uk>
\item Frank Loeffler <knarf@cct.lsu.edu>
\item James Hetherington <j.hetherington@ucl.ac.uk>
\item "Sou-Cheng (Terrya) Choi" <sou.cheng.terrya.choi@gmail.com>
\item James Howison <james@howison.name>
\item Bruce Berriman <gbb@ipac.caltech.edu>
\item Hilmar Lapp <hlapp@nescent.org>
\item "Marcus D. Hanwell" <marcus.hanwell@kitware.com>
\item Lucas Nussbaum <lucas.nussbaum@loria.fr>
\item Matthew Turk <matthewturk@gmail.com>
\end{itemize}

The original document is \url{https://docs.google.com/document/d/1eVfioGNlihXG_1Y8BgdCI6tXZKrybZgz5XuQHjT1oKU/edit?pli=1#} (but can no longer be edited).
Note that the original document has comments in addition to text.

\pagebreak

\section*{Executive Summary}

\pagebreak

@@

...

\section{Agenda}

\section{Keynotes}

what was presented and what was discussed

\section{Developing and Supporting Software}

what was presented and what was discussed

\section{Policy}

what was presented and what was discussed

\section{Communities}

what was presented and what was discussed

\section{Other Discussion}

from the misc questions/answers/observations part of the google doc?

\section{Cross-cutting Issues}

pull the discussion together

\subsection{Recommendations or Lessons}

if needed.

\subsection{Follow up actions}

or at least the discussion about them, and the current plans for future events.

\section{Pre-workshop section: Introduction}

@@

\section{Pre-workshop section: Submissions}

@@

\section{Pre-workshop section: Peer-Review}

@@

\section{Pre-workshop section: Results}

@@

\section{Pre-workshop section: Conclusions}
